SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-08 results.tex
FINAL(?)

\noindent \textbf{4-Core:} Figure~\ref{Fig:4Core_SPEC2017}
shows a comparison of speedups obtained on 4-core mixes of a memory
intensive subset SPEC CPU 2017. We plot all 4 prefetchers, normalized
to the baseline. The workloads have been sorted in increasing order of
the speedup. PPF offers a speedup of \textbf{51.2\%} on these traces,
an improvement of \textbf{11.4\%} over the underlying SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not
illustrated for space reasons), PPF provides an IPC speedup of
\textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.

@@

Figure~\ref{Fig:CrossVal}(b) shows the speed-up achieved on the memory
intensive subset and the full SPEC CPU 2006 suite for a
single-processor machine.  PPF provides a speedup of \textbf{36.3\%}
over the baseline on the memory intensive subset of SPEC CPU 2006
benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole
of the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an
improvement of \textbf{3.33\%} over SPP.

>>>>

\noindent \textbf{4-Core:} Figure~\ref{Fig:4Core_SPEC2017}
shows a comparison of speedups obtained on 4-core mixes of a memory
intensive subset of SPEC CPU 2017. We plot all 4 prefetchers, normalized
to the baseline. The workloads have been sorted in increasing order of
the speedup. PPF offers a speedup of \textbf{51.2\%} on these traces,
an improvement of \textbf{11.4\%} over the underlying SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not
illustrated for space reasons), PPF provides an IPC speedup of
\textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.

@@

Figure~\ref{Fig:CrossVal}(b) shows the speed-up achieved on the memory
intensive subset and the full SPEC CPU 2006 suite for a
single-processor machine.  PPF provides a speedup of \textbf{36.3\%}
over the baseline on the memory intensive subset of SPEC CPU 2006
benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93\%} over BOP. On the whole
of the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an
improvement of \textbf{3.33\%} over SPP.
